% Appendix C

\chapter{Proofs to theorems in \ref{Chapter4}} % Main appendix title

\label{Appendix_D} % For referencing this appendix elsewhere, use \ref{AppendixD}


\begin{thm*}(Gale-Shapley)
The matching given by DA mechanism is stable.
\end{thm*}

\begin{proof}
We will prove it by reduction to absurdity. Suppose not, then there is
a student $i$ and  a college $j$  such that $i$ strictly prefers $j$ to his
final assignment and $|\mu^{-1}(j)|< q_j\ or\  \exists i' \in
\mu^{-1}(j)\  satisfying\ \pi_{j}(i') < \pi_{j}(i)$.  However,
according to the student side operation of DA mechanism,  $j$ must have been applied before the
final assignment college. And  according to the college side operation
of DA mechanism, if  $|\mu^{-1}(j)|< q_j\ or\  \exists i' \in
\mu^{-1}(j)\  satisfying\ \pi_{j}(i') < \pi_{j}(i)$, then $i$ must not
be rejected by $j$ which contradicts to the fact that he or she was
rejected(implied by the fact that his or her final college is lower in
the application order than college $j$).
\end{proof}
\begin{thm*}(Gale-Shapley)
Every student is at least as well off under the assignment given by
the DA mechanism as he would be under any other stable assignment.
\end{thm*}

\begin{proof}
Call a college $j$ achievable for a student $i$ in a particular
environment if the student can be assigned the college in some stable
matching result. 

The proof is to show the following proposition. Up to a certain step $ n $, no student has ever
been rejected by a college achievable for the student, then no student
will be rejected by a college achievable for the student in the step
$n$ too. 

Since up to step $1$, no student has been rejected by any
college obivously, we can show that up to  any finite step no student
will ever be rejected by  a college achievable for the student by
repeatedly applying the previous proposition.  The
end step is a finite number, so in the final result no student is ever
rejected by a college achievable for the student. And the students apply colleges from the most favorite to the least favorite, we therefore know that the final assignment is most favorite for every
student among the stable matchings.

Now we will prove that up to a certain step $ n $, no student has ever
been rejected by a college achievable for the student, then no student
will be rejected by a college achievable for the student in the step
$n$ too.  
%We will do it by way of reduction to absurdity. 
That is
eqivalent to
say, suppose a
student $i$ is rejected by a college  $j$ in the
step $n$, then the college is not achievable for the student. Since
$j$ reject $i$, that means that  after
step $n$ every student assigned to $j$ is higher in priority than $i$,
and the quota of $j$ has been full. If $i$ is assigned to $j$ in some
stable 
matching result, then some $i'$ that is assigned to $j$ in the step
$n$ must be assigned to some college that is less preferred than $j$
because up to $n$ no student is rejected by an achievable college. A
contradiction occurs here for such a matching result cannot be
a stable matching result due to the existence of pair $i', j $ which
blocks $i, j$. Therefore by reduction to absurdity,  we show that $i$
cannot be assigned to $j$  in any stable matching result, i.e., $j$ is
not achievable to$i$.
\end{proof}

%See \parencite{Gale1962} for more details.


